---
title: "Visualization with ggplot2"
author: "Ruixi Li"
date: "2023-09-28"
output: html_document
---

```{r setup, message=FALSE}
library(tidyverse)
library(ggridges)
```

## load the  weather data

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USW00022534", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2021-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Molokai_HI",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())

weather_df
```

## Scatterplots

first scatterplot ever

```{r}
ggplot(weather_df,aes(x = tmin, y = tmax)) +
  geom_point()

```
New proach, same plot

```{r}

  weather_df |> 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point()
```
save and edit plot objects
```{r}
weather_plot = weather_df |> 
  ggplot(aes(x = tmin, y = tmax))

weather_plot + geom_point()
```


## Advanced scatterplot

```{r}
weather_df |> 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point() +
  geom_smooth(se = FALSE)
```
three lines with different colors
what about the `aes` replacement...?

```{r}
weather_df |> 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(aes(color = name)) +
  geom_smooth()
```
only one blue line



lets facet some thing
```{r}
weather_df |> 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point() +
  geom_smooth(se = FALSE)
  facet_grid(. ~ name)# divide by name into columns,when revert . and name <-  divide by name into rows;also can replace . with other variables
```


```{r}
weather_df |> 
  ggplot(aes(x = tmin, y = tmax,alpha = tmin, color = name)) +
  geom_point(size =0.2) +
  geom_smooth(se = FALSE) +
  facet_grid(. ~ name)
```
* alpha=tmin adjust transparency-left is more transparent than right
* alpha=tmax adjust transparency-down is more transparent than up
*alpha=0.2, setup in geom_point() to serve as a global option,transparency =0.2


combine some elements and plot them

```{r}
ggplot(weather_df, aes(x = date, y = tmax, color = name)) + 
  geom_point(aes(size = prcp), alpha = .5) +
  geom_smooth(se = FALSE) + 
  facet_grid(. ~ name)
```

## some small notes
you can have whatever geoms you want.
```{r}
ggplot(weather_df, aes(x = date, y = tmax, color = name)) + 
  geom_smooth(se = FALSE) 
```


```{r}
ggplot(weather_df, aes(x = tmax, y = tmin)) + 
  geom_hex()#蜂巢


ggplot(weather_df, aes(x = tmax, y = tmin)) + 
  geom_bin2d()#square

ggplot(weather_df, aes(x = tmax, y = tmin)) + 
  geom_density2d()#等线图
```

## univariate plots

```{r}
weather_df |> 
  ggplot(aes(x = tmin, fill = name)) +
  geom_histogram(size =0.2) + 
  facet_grid(. ~ name)

weather_df |> 
  ggplot(aes(x = tmin, fill = name)) +
  geom_histogram(position = "dodge") 
```



let's try a new geomtry

```{r}
weather_df |> 
  ggplot(aes(x = tmin, fill = name)) +
  geom_density(alpha = 0.3, adjust=0.5) 
```
density plot will lose some information(little bumps),using `adjust` may help rescue



boxplot


```{r}

weather_df |>
  ggplot(aes(x = name, y = tmin)) + 
  geom_boxplot()
```






trendy plots


```{r}
weather_df |>
  ggplot(aes(x = name, y = tmin, fill=name)) + 
  geom_violin() +
  stat_summary()
```



ridge plots- the most  popular plot in 2017

```{r}
weather_df |>
  ggplot(aes(x = tmin, y = name, fill=name)) + 
  geom_density_ridges()

```
it's very nice to use rideg plots when you have 40-50 categories.

## save and embed

```{r}
ggsave("weather_plot.png",weather_plot, width=8, height =5)
```

embed
```{r}
weather_plot =
  weather_df |> 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point() +
  geom_smooth(se = FALSE)

```


embed at a different size

```{r fig.width= 12,fig.height=6}
weather_plot
```

